Proof No Diamond (3 layers)

### 2024-04-16 lipics-master/proofs.tex
update

Notice that above definitions only involve weights, not bias. From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.

@@

@@

>>>>

{\color{red}Notice that above definitions only involve weights, not bias. From the following lemmas and proofs, we can find that our discussion is irrelevant to bias, no matter the bias are very large positive or negative, or very close to 0.}

@@

							{ \color{red}	Similarly, above definitions $A_{zero},A_{open}, A_{pure}$ and $B_{zero},B_{open},B_{pure}$ do not involve bias, and any kind of bias will not influence our theorem.}

@@

{\color{red} In all above statements and proofs, we do not use any assumption of bias, and the bias will have no influence on our discussion. }
